\begin{thebibliography}{1}
	\bibitem aStatista, The Statistics Portal. Smartphone users worldwide 2014-2020, 2017. [Online; Julho, 2017]. Available: \href{https://www.statista.com/statistics/330695/number-of-smartphone-users-worldwide/}{https://www.statista.com/statistics/330695/number-of-smartphone-users-worldwide/}.
	\label{estatiscasmart}
	
	%% Referências da tabela dos transmissores [INÍCIO]
	\bibitem aRoger Technology. Serie E80 RADIOCOMANDI. [Online]. Available: \href{http://www.rogertechnology.com/ita/e80tx52r2-376.asp}{http://www.rogertechnology.com/ita/e80tx52r2-376.asp}.
	\label{rogercomando}
	\bibitem aEsma Remote Control. CLEMSA MUTANCODE T2 Remote control. [Online]. Available: \href{http://www.remote-control-esma.com/clemsa-mutancode-t2-remote-control/}{http://www.remote-control-esma.com/clemsa-mutancode-t2-remote-control/}.
	\label{mutancodecomando}
	\bibitem aJCM Technologies. Access units, GO 868 MHz transmitters. [Online]. Available: \href{https://www.jcm-tech.com/downloads/PS_EA806_GO_EN.pdf}{https://www.jcm-tech.com/downloads/PS\_EA806\_GO\_EN.pdf}.
	\label{jcmcomando}
	\bibitem aAutomatismos Pujol, Somfy Group. Vario remote controll. [Online]. Available: \href{http://www.automatismospujol.es/arxiusdb/pdf/articles/96_manual.pdf}{http://www.automatismospujol.es/arxiusdb/pdf/articles/96\_manual.pdf}.
	\bibitem aRemote4gates. NORTON TXCD4 ME Remote control. [Online]. Available: \href{http://remote4gates.com/norton-txcd4-me-remote-control/}{http://remote4gates.com/norton-txcd4-me-remote-control/}.
	\bibitem aRemote control express. ROPER TX2 OLD. [Online]. Available: \href{http://www.remotecontrol-express.co.uk/remote+ROPER+:+TX2+OLD}{http://www.remotecontrol-express.co.uk/remote+ROPER+:+TX2+OLD}.
	\bibitem aERREKA Automatismos. IRIS, Emisor Roller Code. [Online]. Available: \href{http://www.erreka-automation.com/upload/productos_descargas/IR02.pdf}{http://www.erreka-automation.com/upload/productos\_descargas/IR02.pdf}.
	\bibitem aCELINSA Automatismos para Puertas. EMISORES. [Online]. Available: \href{http://www.celinsa.es/celinsa-emisores-y-receptores.html}{http://www.celinsa.es/celinsa-emisores-y-receptores.html}.
	\bibitem aEasyGates. Aprimatic Remote Controls. [Online]. Available: \href{http://www.easygates.co.uk/aprimatic-tr2-remote-control.asp}{http://www.easygates.co.uk/aprimatic-tr2-remote-control.asp}.
	\bibitem aDEA, move as you like. REMOTE CONTROLS. [Online]. Available: \href{http://www.deasystem.com/en/accessory/8/remote-controls}{http://www.deasystem.com/en/accessory/8/remote-controls}.
	\bibitem aEasyGates, Manuals. Flo Transmitter. [Online]. Available: \href{http://manuals.easygates.co.uk/PDF/misc/D00010129.pdf}{http://manuals.easygates.co.uk/PDF/misc/D00010129.pdf}.
	\bibitem aBeninca, Technology to open. EMISSORES TO.GO ARC K. [Online]. Available: \href{http://www.beninca.com/pt/accessori/trasmettitori/togo-arc-k.html}{http://www.beninca.com/pt/accessori/trasmettitori/togo-arc-k.html}.
	\bibitem aSeav. RADIO CONTROL  BEHAPPY SERIES ``S'' NEW. [Online]. Available: \href{http://www.seav.it/sites/default/files/prodotti/schede_tecniche/BeHappy\%20S\%201-2-3\%20New\%20GB_0.pdf}{http://www.seav.it/sites/default/files/prodotti/schede\_tecniche/BeHappy\%20S\%201-2-3\%20New\%20GB\_0.pdf}.
	\bibitem aBft, Be ahead. KLEIO. [Online]. Available: \href{https://www.bft-automation.com/pt_PT/detalhe-familia/telecomandos-rolling-code-433-mhz-com-acabamentos-soft-touch-kleio/\#kleio-b-rca02-r1}{https://www.bft-automation.com/pt\_PT/detalhe-familia/telecomandos-rolling-code-433-mhz-com-acabamentos-soft-touch-kleio/\#kleio-b-rca02-r1}.
	\bibitem aEasyGates, Manuals. PHOENIX. [Online]. Available: \href{http://manuals.easygates.co.uk/PDF/v2/phoenix.pdf}{http://manuals.easygates.co.uk/PDF/v2\\/phoenix.pdf}.
	\bibitem aEasyGates, Manuals. BIXLR12-22 - GOL. [Online]. Available: \href{http://manuals.easygates.co.uk/PDF/ditec/BIXLR12-22-GOL_IP2016.pdf}{http://manuals.easygates.co.uk/PDF/ditec/BIXLR12-22-GOL\_IP2016.pdf}.
	\bibitem aRemote pro. Nice Flor-S Compatible Remote. [Online]. Available: \href{https://www.remotepro.com.au/products/nice-flor-s-remote}{https://www.remotepro.com.au/products/nice-flor-s-remote}.
	\bibitem aMotorline professional. MX4SP. [Online]. Available: \href{http://web.electrocelos.com:81/download/manuais/eletronica/mx4_pt.pdf}{http://web.electrocelos.com:81/download\\/manuais/eletronica/mx4\_pt.pdf}.
	\bibitem aEasyGates, Manuals. 868 SLH SYSTEM. [Online]. Available: \href{http://manuals.easygates.co.uk/PDF/misc/200_Manual_rad2C181.pdf}{http://manuals.easygates.co.uk/PDF/misc/200\_Manual\_rad2C181.pdf}.
	\bibitem aEasyGates, Manuals. TOP 432 NA. [Online]. Available: \href{http://manuals.easygates.co.uk/PDF/CAME/T74v01\%20-\%20Top\%20432\%20NA.pdf}{http://manuals.easygates.co.uk/PDF/CAME/T74v01\%20-\%20Top\%20432\%20NA.pdf}.
	\bibitem aEasyGates, Manuals. GTX4 - GTX4C. [Online]. Available: \href{http://manuals.easygates.co.uk/PDF/misc/GTX4-GTX4.pdf}{http://manuals.easygates.co.uk/PDF/misc/GTX4-GTX4.pdf}.
	%% Referências da tabela dos transmissores [FIM]
	
	\bibitem a[Online]. Available: \href{https://images-na.ssl-images-amazon.com/images/I/81G5FLhUuRL._SL1500_.jpg}{https://images-na.ssl-images-amazon.com/images/I/81G5FLhUuRL.\\\_SL1500\_.jpg}.
	\label{motorlineremotelink}
	\bibitem a[Online]. Available: \href{https://www.fastaccesssecurity.com/prodimages/BFT-MITTO-250.jpg}{https://www.fastaccesssecurity.com/prodimages/BFT-MITTO-250.jpg}.
	\label{bftremotelink}
	\bibitem a[Online]. Available: \href{http://www.lockitup.com.au/wp-content/gallery/garage-remotes/rdt01.jpg}{http://www.lockitup.com.au/wp-content/gallery/garage-remotes/rdt01.jpg}.
	\label{ditecremotelink}
	
	%% Referências da tabela dos recetores [INÍCIO]
	\bibitem aRoger Technology. Series H93  RADIO RECEIVERS. [Online]. Available: \href{http://www.rogertechnology.com/eng/h93rx22ai-418.asp}{http://www.rogertechnology.com/eng/h93rx22ai-418.asp}.
	\bibitem aRoger Technology. Series H93 RADIO RECEIVERS. [Online]. Available: \href{http://www.rogertechnology.com/eng/h93rx2rci-1306.asp}{http://www.rogertechnology.com/eng/h93rx2rci-1306.asp}.
	\bibitem aRoger Technology. Series R93 RADIO RECEIVERS. [Online]. Available: \href{http://www.rogertechnology.com/eng/r93rx14m24-502.asp}{http://www.rogertechnology.com/eng/r93rx14m24-502.asp}.
	\bibitem aBft, Be ahead. CLONIX 2E AC U-LINK 230. [Online]. Available: \href{https://www.bft-automation.com/pt_PT/produto/?tx_productmanager_productviewer\%5Bproduct\%5D=917\&cHash=7782861e301dc4e75273ffd2771cfd9e}{https://www.bft-automation.com/pt\_PT/produto/?tx\_productmanager\_productviewer\%5Bproduct\%5D=917\\\&cHash=7782861e301dc4e75273ffd2771cfd9e}.
	\bibitem aBft, Be ahead. CLONIX UNI AC U-LINK 230 V. [Online]. Available: \href{https://www.bft-automation.com/pt_PT/produto/?tx_productmanager_productviewer\%5Bproduct\%5D=918\&cHash=8c06412501e958d43199706301d76c7c}{https://www.bft-automation.com/pt\_PT/produto/?tx\_productmanager\_productviewer\%5Bproduct\%5D=918\\\&cHash=8c06412501e958d43199706301d76c7c}.
	\bibitem aBft, Be ahead. CLONIX 4 RTE. [Online]. Available: \href{https://www.bft-automation.com/pt_PT/produto/?tx_productmanager_productviewer\%5Bproduct\%5D=919\&\\cHash=af2f05033a41da8f47290f0492c04fd3}{https://www.bft-automation.com/pt\_PT/produto/?tx\_productmanager\_productviewer\%5Bproduct\%5D=919\\\&cHash=af2f05033a41da8f47290f0492c04fd3}.
	\bibitem aAutomatismos Pujol, Somfy Group. junior D Pro. [Online]. Available: \href{http://www.automatismospujol.es/arxiusdb/pdf/articles/83_manual.pdf}{http://www.automatismospujol.es/arxiusdb/pdf/articles/83\_manual.pdf}.
	\bibitem aDama, centrum kovovýroby. FAST R2 GB.[Online]. Available: \href{https://www.idama.cz/ew/a6f53d17-6f32-4214-9b27-50a361bc6b0e-cs}{https://www.idama.cz/ew/a6f53d17-6f32-4214-9b27-50a361bc6b0e-cs}.
	\bibitem aDama, centrum kovovýroby. DIGITAL LIFE TECHNOLOGY.[Online]. Available: \href{https://www.idama.cz/ew/aa9ce69b-c3fb-4f23-8d45-9f7df7f2920a-cs}{https://www.idama.cz/ew/aa9ce69b-c3fb-4f23-8d45-9f7df7f2920a-cs}.
	\bibitem aDitec entrematic. Ditec BIXLR22 - BIXLR42 - GOL868R4 - Self-learning PCB receiver.[Online]. Available: \href{http://www.ditecentrematic.com/products/accessories/control/bixlr22-bixlr42-gol868r4}{http://www.ditecentrematic.com/products/accessories/control/bixlr22-bixlr42-gol868r4}.
	\bibitem aDitec entrematic. Ditec BIXLR22 - BIXLR42 - GOL868R4 - Self-learning PCB receiver.[Online]. Available: \href{http://www.ditecentrematic.com/products/accessories/control/bixlr22-bixlr42-gol868r4}{http://www.ditecentrematic.com/products/accessories/control/bixlr22-bixlr42-gol868r4}.
	\bibitem aDitec entrematic. Ditec BIXLR22 - BIXLR42 - GOL868R4 - Self-learning PCB receiver.[Online]. Available: \href{http://www.ditecentrematic.com/products/accessories/control/bixlr22-bixlr42-gol868r4}{http://www.ditecentrematic.com/products/accessories/control/bixlr22-bixlr42-gol868r4}.
	\bibitem aDownee. NET230N Operating Instructions.[Online]. Available: \href{http://www.downee.com.au/Media/Default/installation_guides/automation/NET230N-programming-instructions.pdf}{http://www.downee.com.au/Media/Default/installation\_guides/automation/NET230N-programming-instructions.pdf}.
	\bibitem aAutogate. BENINCA ONE.2WI Plug-in Radio Receiver.[Online]. Available: \href{https://www.autogate.eu/beninca-one2wi-plug-in-radio-receiver-p-1283.html}{https://www.autogate.eu/beninca-one2wi-plug-in-radio-receiver-p-1283.html}.
	\bibitem aAutogate. Odbiornik 2-kanalowy ONE.2QI Beninca.[Online]. Available: \href{https://emarket-automatyka.pl/akcesoria-do-napedow-odbiorniki-radiowe/1480-odbiornik-2-kanalowy-one2qi-beninca.html}{https://emarket-automatyka.pl/akcesoria-do-napedow-odbiorniki-radiowe/1480-odbiornik-2-kanalowy-one2qi-beninca.html}.
	\bibitem aJCM Technologies. BASELEC500.[Online]. Available: \href{https://www.jcm-tech.com/JCM/baselec500/}{https://www.jcm-tech.com/JCM/baselec500/}.
	\bibitem aQualified hardware. 433 MHz TRANSMITTERS \& RECEIVER USER'S GUIDE.[Online]. Available: \href{http://www.qualifiedhardware.com/downloads/Instructions\%20539.pdf}{http://www.qualifiedhardware.com/downloads/Instructions\%20539.pdf}.
	\bibitem aERREKA Automatismos. RECEPTOR INDEPENDENTE.[Online]. Available: \href{http://www.erreka-automation.com/upload/productos_descargas/IRIN4B.pdf}{http://www.erreka-automation.com/upload/productos\_descargas/IRIN4B.pdf}.
	\bibitem aCELINSA Automatismos para Puertas. RECEPTORES.[Online]. Available: \href{http://www.celinsa.es/celinsa-emisores-y-receptores.html}{http://www.celinsa.es/celinsa-emisores-y-receptores.html}.
	\bibitem aSeav. RXX 2224 DUAL CHANNEL RECEIVER.[Online]. Available: \href{http://www.seav.it/sites/default/files/prodotti/schede_tecniche/Rxx\%202224\%20GB.pdf}{http://www.seav.it/sites/default/files/prodotti/schede\_tecniche/Rxx\%202224\%20GB.pdf}.
	\bibitem aEasyGates, Manuals. RXX 2167 .[Online]. Available: \href{http://manuals.easygates.co.uk/PDF/misc/Rxx-2167-GB_0.pdf}{http://manuals.easygates.co.uk/PDF/misc/Rxx-2167-GB\_0.pdf}.
	\bibitem aV2, Value moves the world. RXP4. [Online]. Available: \href{http://www.v2elettronica.com/product.php?lang=en\&id=44\&id_cat=7}{http://www.v2elettronica.com/product.php?lang=en\&id=44\&id\_cat=7}.
	\bibitem aV2, Value moves the world. RXP4. [Online]. Available: \href{http://www.v2elettronica.com/product.php?lang=en\&id=44\&id_cat=7}{http://www.v2elettronica.com/product.php?lang=en\&id=44\&id\_cat=7}.
	\bibitem aInforsolutions. GateControl GSM. [Online]. Available: \href{http://www.inforsolutions.pt/galeria/GateControl\%201000\%20Manual\%20PT.pdf}{http://www.inforsolutions.pt/galeria\\/GateControl\%201000\%20Manual\%20PT.pdf}.
	%% Referências da tabela dos recetores [FIM]
	
	\bibitem a[Online]. Available: \href{http://motorline.pt/wp-content/uploads/2016/12/RTX2251-1.jpg}{http://motorline.pt/wp-content/uploads/2016/12/RTX2251-1.jpg}.
	\label{motorlinereceiverlink}
	\bibitem a[Online]. Available: \href{http://www.rogertechnology.com/public/img/gestionesezioni/img_2652014112932.jpg}{http://www.rogertechnology.com/public/img/gestionesezioni/img\\\_2652014112932.jpg}.
	\label{rogerreceiverlink}
	\bibitem a[Online]. Available: \href{https://www.bft-automation.com/fileadmin/_processed_/csm_deimos_A_BT_fronte_ultra_3996268802.png}{https://www.bft-automation.com/fileadmin/\_processed\_/csm\_deimos\_A\\\_BT\_fronte\_ultra\_3996268802.png}.
	\label{bftreceiverlink}
	
	\bibitem aMicrochip. HCS301, KEELOQ Code Hopping Encoder [Online]. Available: \href{http://ww1.microchip.com/downloads/en/DeviceDoc/21143b.pdf}{http://ww1.microchip.com/downloads/en/DeviceDoc/21143b.pdf}.
	\label{hcs301}
	\bibitem aDatasheetsPDF. EV1527 Datasheet PDF - Silvan Chip [Online]. Available: \href{http://www.datasheet-pdf.com/PDF/EV1527-Datasheet-SilvanChip-688412}{http://www.datasheet-pdf.com/PDF/EV1527-Datasheet-SilvanChip-688412}.
	\label{ev1527}
	\bibitem a[Online]. Available: \href{http://desembola.com/wp-content/uploads/2017/05/contemporary-decoration-dip-switch-garage-door-remote-merry-fadini-control-transmitters.jpg}{http://desembola.com/wp-content/uploads/2017/05/contemporary-decoration-dip-switch-garage-door-remote-merry-fadini-control-transmitters.jpg}.
	\label{dipremote}
	\bibitem aJMA, Altuna Portugal. Comandos SR-4V , SR-48, SR-Q [Online]. Available: \href{http://www.jmaportugal.com/Archivos/productos/manual_comandos_pt_v02.pdf}{http://www.jmaportugal.com/Archivos/productos/manual\_comandos\_pt\_v02.pdf}.
	\label{jmalink}
	
	\bibitem aInfineon. IFX91041, 1.8A DC/DC Step-Down Voltage Regulator [Online]. Available: \href{https://www.infineon.com/dgdl/Infineon-IFX91041-DS-v01_01-en.pdf?fileId=db3a304320d39d59012153afb91a0548}{https://www.infineon.com/dgdl/Infineon-IFX91041-DS-v01\_01-en.pdf?fileId=db3a304320d39d59012153afb91a0548}.
	\label{stepdown}
	\bibitem aMornsun. B0505S, 1W, FIXED INPUT ISOLATED \& UNREGULATED
	SINGLE OUTPUT MINIATURE SIP/DIP PACKAGE [Online]. Available: \href{http://mornsun-power.com/pdf/DCDC\%20Converter/B_S-1W.pdf}{http://mornsun-power.com/pdf/DCDC\%20Converter/B\_S-1W.pdf}.
	\label{isolado}
	\bibitem aTexas Instruments. REG1117, 1W, 800mA and 1A Low Dropout Positive Regulator [Online]. Available: \href{http://www.ti.com/lit/ds/sbvs001d/sbvs001d.pdf}{http://www.ti.com/lit/ds/sbvs001d/sbvs001d.pdf}.
	\label{33pdf}
	\bibitem aMicrochip. PIC18F87K22 Family Data Sheet [Online]. Available: \href{http://ww1.microchip.com/downloads/en/DeviceDoc/39960d.pdf}{http://ww1.microchip.com/downloads/en/DeviceDoc/39960d.pdf}.
	\label{picpdf}
	\bibitem aAi-Thinker[Online]. Available: \href{http://wiki.ai-thinker.com/_media/gprs/docs/aithinker_a6_a7_a6c_a20_user_manual_20170208.pdf}{http://wiki.ai-thinker.com/\_media/gprs/docs/aithinker\_a6\_a7\_\\a6c\_a20\_user\_manual\_20170208.pdf}.
	\label{gsmpdf}
	\bibitem a[Online]. Available: \href{http://img.dxcdn.com/productimages/sku_433790_2.jpg}{http://img.dxcdn.com/productimages/sku\_433790\_2.jpg}.
	\label{gsmimagem}
	\bibitem aSemtech. Low Power Integrated UHF Transceiver. [Online]. Available: \href{http://www.semtech.com/images/datasheet/sx1231_ag.pdf}{http://www.semtech.com/images/datasheet/sx1231\_ag.pdf}.
	\label{sx1231pdf}
	\bibitem aIEEE Xplore Digital Library. [Online]. Available: \href{http://ieeexplore.ieee.org/Xplore/home.jsp}{http://ieeexplore.ieee.org/Xplore/home.jsp}.
	\label{ieee}

	
	\bibitem aIEEE Xplore Digital Library. Dual UHF RFID band miniaturized multipurpose planar antenna for compact wireless systems. [Online]. Available: \href{http://ieeexplore.ieee.org/document/5464676/}{http://ieeexplore.ieee.org/document/5464676/}.
	\label{paperantena1}
	\bibitem aIEEE Xplore Digital Library. A Small Implantable Antenna for MedRadio and ISM Bands. [Online]. Available: \href{http://ieeexplore.ieee.org/document/6415980/}{http://ieeexplore.ieee.org/document/6415980/}.
	\bibitem aIEEE Xplore Digital Library. Design and measurement of a planar dual-band antenna for the Tyndall Multiradio wireless sensing platform. [Online]. Available: \href{http://ieeexplore.ieee.org/document/6493548/}{http://ieeexplore.ieee.org/document/6493548/}.
	\bibitem aIEEE Xplore Digital Library. Design and Analysis of a Dual-Band Inverted-F Antenna With Orthogonal Frequency-Controlled Radiation Planes. [Online]. Available: \href{http://ieeexplore.ieee.org/document/6509414/}{http://ieeexplore.ieee.org/document/6509414/}.
	\bibitem aIEEE Xplore Digital Library. Set of new compact antennas suitable for integration on PCB. [Online]. Available: \href{http://ieeexplore.ieee.org/document/6996315/}{http://ieeexplore.ieee.org/document/6996315/}.
	\bibitem aIEEE Xplore Digital Library. Miniaturized meander PCB antenna for 433MHz. [Online]. Available: \href{http://ieeexplore.ieee.org/document/7509138/}{http://ieeexplore.ieee.org/document/7509138/}.
	\bibitem aSlidePlayer. Practical Radio design. [Online]. Available: \href{http://slideplayer.com/slide/1554966/}{http://slideplayer.com/slide/1554966/}.
	\bibitem aTexas Instruments. Application Note AN058. [Online]. Available: \href{http://www.ti.com/lit/an/swra161b/swra161b.pdf}{http://www.ti.com/lit/an/swra161b/swra161b.pdf}.
	\bibitem aTexas Instruments. Design Note DN031. [Online]. Available: \href{http://www.ti.com/lit/an/swra328/swra328.pdf}{http://www.ti.com/lit/an/swra328/swra328.pdf}.
	\bibitem aTexas Instruments. Design Note DN038. [Online]. Available: \href{http://www.ti.com/lit/an/swra416/swra416.pdf}{http://www.ti.com/lit/an/swra416/swra416.pdf}.
	\bibitem aTexas Instruments. Antenna Selection Quick Guide DN035. [Online]. Available: \href{http://www.ti.com/lit/an/swra351a/swra351a.pdf}{http://www.ti.com/lit/an/swra351a/swra351a.pdf}.
	\label{appnoteantena2}
	
	
	
	
	\bibitem aSaturn PCB design. Turnkey Eletronic Engineering Solucions[Online]. Available: \href{http://www.saturnpcb.com/pcb_toolkit.htm}{http://www.saturnpcb.com/pcb\_toolkit.htm}.
	\label{saturn}
\end{thebibliography}\vfill\pagebreak\thispagestyle{plain}